Evaluation of the repository

### 2024-11-21 pages/repo_evaluation.qmd
chore(badges): save to csv

# Replace with full badge names, then filter and relabel columns
badges_table.index = badges_table.index.map(badge_names)
badges_table.index.name = 'Badge'
badges_table = badges_table[['criteria', 'met_criteria']].rename(
  columns={'criteria': 'Criteria', 'met_criteria': 'Studies that met criteria'}
)
badges_table
```

>>>>

# Replace with full badge names, then filter and relabel columns
badges_table.index = badges_table.index.map(badge_names)
badges_table.index.name = 'Badge'
badges_table = badges_table[['criteria', 'met_criteria']].rename(
  columns={'criteria': 'Criteria', 'met_criteria': 'Studies that met criteria'}
)

# Save to CSV and show
badges_table.to_csv('../data/badges_table.csv')
badges_table
```
